---
title: "emojifun: An R Package for Emoji & Pokémon Visualization"
output: html_document
date: "2025-04-28"
---
### Jiaying Chen
### ESRM 699V
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## 💬 Background information

- Emojis are widely used for **communication** and **sentiment expression** in text.
- Pokémon are culturally iconic and **visually engaging**, especially in educational or playful visualizations.
- Combining text and images adds a **fun, interactive layer** to data analysis and reporting in R.

➡️ But R lacks built-in tools for converting text to emoji and inserting character images like Pokémon in R Markdown or console.




## ❗ Problem Statement

- R users often want to **visualize** or **enrich** outputs using emojis or **visual media** like images and GIFs, but the available tools for these tasks are limited and complex..
- Emoji conversion is **manual** and limited.
- Inserting character graphics (like Pokémon) into R Markdown is not straightforward.
- There’s a gap in tools that are:
  - **Easy to use** without requiring complex coding skills.
  - **Markdown-ready** for smooth integration into reports and presentations.
  - **Fun and functional**, adding value beyond basic data visualization.




## 🎯 Goal of `emojifun`

To create an **easy-to-use R package** that lets users:

- Automatically convert **text to emoji** based on meaning.
- Insert **Pokémon images** into R Markdown.
- Customize and expand emoji/image dictionaries easily.

All designed to **enhance presentations, reports, or playful projects**.




## 📦 Package Components
The `emojifun` package provides the following main functions and internal support:

- `tte()` – Converts text to emojis.
- `newtte()` – Converts text to emojis(random pick).
- `show_pokemon()` – Inserts Pokémon images (PNG).
- `mbtie()` – Inserts MBTI images (PNG).


Internal Support:

- Custom Emoji Dictionary (JSON-based): Users can easily expand or customize the available emoji set by providing a JSON file that maps words to specific emojis. 
- Pokémon Sprite Mapping: Includes a mapping of Pokémon names to their corresponding image files, making it straightforward to call and display Pokémon characters within R Markdown.




## 🧠 Text-to-Emoji Function

```{r}
library(emojifun)
tte("I am happy") 
tte("I like dog and cat")

```


```{r}
library(emojifun)
newtte("I like dog and cat")
```
```{r}
library(emojifun)
newtte("today is a sunny day, i wanna go outside with my friends") 
newtte("i feel sad because our team failed in the basketball game") 
newtte("which animals is in the picture? gorilla, monkey, panda, dolphin, rabbit  ?")
newtte("I love pizza and chocolate!")

```

## 🧸 pokemon Function

```{r}
library(emojifun)
show_pokemon("pikachu")

```


I like
```{r, echo=FALSE}
show_pokemon("charmander")
```
very much!



```{r, echo=FALSE}
mbtie("ISTP")

```


## ⚙️ resources

- `emoji-en-US.json` from [emojilib](https://github.com/muan/emojilib)
- `pokemon.csv` parsed from PokéAPI sprite data
- Handles file lookup, path resolution, and fallback errors
- Modular and extensible codebase




## ✅ Summary

- `emojifun` makes R more expressive and fun
- Solves emoji and image-insertion problems in a simple way
- Useful for:
  - Education
  - Presentations
  - Shiny apps
  - Just having fun with R!

Thank you! 🙏

